
%---------------------------------------------------------------------------%
%->> Frontmatter
%---------------------------------------------------------------------------%
%-
%-> 生成封面
%-

\maketitle% 生成中文封面
\MAKETITLE% 生成英文封面
%-
%-> 作者声明
%-
\makedeclaration% 生成声明页
%-
%-> 中文摘要
%-


\intobmk\chapter*{摘\quad 要}% 显示在书签但不显示在目录
\setcounter{page}{1}% 开始页码
\pagenumbering{Roman}% 页码符号

双有理代数几何的目标之一是双有理等价分类代数簇，极小模型纲领用来在每一个固定的双有理等价类中找到一个良好的代表元。
所有这些代表元可以分为两类，一种称为极小模型，另一种称为森纤维空间，两种代表元都不唯一。
模去自同构后，任何两个MMP-相关的森纤维空间都被一个双有理映射连接，通过运行Sarkisov纲领，可以分解为有限多个基本的双有理映射。这样基本的映射有四种，称为Sarkisov连接。

本文的第一个目标是介绍三种Sarkisov纲领的方法。第二个目标是尝试对叶层化代数簇对建立Sarkisov纲领。通过将$F$-dlt奇点的叶层化代数簇对约化成klt奇点的代数簇对，叶层化森纤维空间之间的双有理映射有较弱的分解。 

\keywords{极小模型纲领，Sarkisov纲领，叶层化对}% 中文关键词
%-
%-> 英文摘要
%-

\intobmk\chapter*{Abstract}% 显示在书签但不显示在目录

One of the goals of birational geometry is to classify varities up to birational equivalence. The minimal model program  is to find a good representative in every fixed birational equivalence class. 
All of these good representatives can be divided into two classes. One is called the minimal model, and the other is called Mori fiber space, both of  which are not unique. 
Moduloing isomorphism, any two MMP-related Mori fibre spaces are connected by a birational map, which can be decomposed into finitely many  elementary birational maps by running the Sarkisov program. There are four types of elementary birational maps, called Sarkisov links.

The first purpose of this paper is to introduce three methods of the Sarkisov program.
The second goal is trying to establish the Sarkisov program for foliated pairs. By reducing $F$-dlt foliated pairs to klt pairs, there is a weak decomposition of birational maps between foliated Mori fibre spaces.  

\KEYWORDS{Minimal Model Program, Sarkisov Program, Foliated pairs}% 英文关键词

% \pagestyle{enfrontmatterstyle}%
\cleardoublepage\pagestyle{frontmatterstyle}%

%---------------------------------------------------------------------------%
