\chapter{绪论}
极小模型纲领(minimal model program, MMP) 的目标是按双有理等价类分类代数簇，并选取选择恰当的代表元。极小模型纲领猜想，每一个代数簇都双有理等价于一个极小模型(minimal model) 或一个森纤维空间(Mori fibre space, mfs)，但这样的代表元有时并不唯一，于是自然的问题就是不同代表元之间的关系。对于极小模型的情形，我们有
\begin{theorem}[平转连接极小模型]
  令$(W,B_{W})$为一个$\mathbb{Q}$-分解的终极对(terminal pair)，且$(X,B_{X}),(Y,B_{Y})$是它的两个极小模型。那么双有理映射$X \dashrightarrow Y$可以分解为一系列$(K_{X}+B_{X})$-平转(flop).
\end{theorem}
对于森纤维空间，由Sarkisov纲领可知
\begin{theorem}[主定理]
  令 $ f:(X, B)\to S$ 和 $f':(X', B')\to S' $ 为两个 MMP-连接的$ \mathbb{Q} $-分解 klt 算术森纤维空间，则有双有理映射 $\Phi$：
  \[
    \xymatrix{
      (X,B)\ar[d]_f\ar@{.>}[r]^\Phi & (X',B')\ar[d]^{f'}\\
      S & S'}
  \]
可以分解为Sarkisov连接映射的复合，即
\[
  \Phi=\Psi_{n}\circ \cdots \circ \Psi_{1}
\]
其中$\Psi_{i}:X_{i}\dashrightarrow X_{i+1} $ 是下列四种Sarkisov连接之一：

  $\textbf{I}$:
  $\xymatrix{
      Z\ar[d]_p\ar@{.>}[r]&X_1\ar[d]^{f_1}\\
      X\ar[d]_f&S_1\ar[dl]^{t}\\
      S &}$
  $\textbf{II}$:
  $\xymatrix{
      Z\ar[d]_p\ar@{.>}[r]&Z'\ar[d]^{q}&\\
      X\ar[d]_{f}&X_1\ar[d]^{f_1}\\
      S\ar[r]^{\sim}&S_1}$

  $\textbf{III}$:
  $
    \xymatrix{
    X\ar@{.>}[r]\ar[d]_f& Z\ar[d]^q& \\
    S\ar[rd]_{s}         & X_{1}\ar[d]^{f_{1}}&\\
    &S_{1}
    }
  $
  $\textbf{IV}$:
  $\xymatrix{
      X\ar[d]_f\ar@{.>}[rr]&&X_1\ar[d]^{f_1}\\
      S\ar[dr]_{s}&&S_1\ar[dl]^{t}\\
      &T &}$

      其中所有$ f:(X, B)\to S $ and $ f_1:(X_1, B_1)\to S_1 $ 都是算术森纤维空间，所有$p,q$ 都是除子压缩，所有虚线的映射都是翻转(flip)、平转(flop)或反向翻转(inverse flip)的复合。
\end{theorem}
在具有叶状结构的代数簇对(foliated pair)上有类似结果：
\begin{theorem}[主定理2]
 TODO 
\end{theorem}
Sarkisov纲领起源于对直纹曲面的分类 \cite{sarkisovBIRATIONALAUTOMORPHISMSCONIC1981}, \cite{sarkisovCONICBUNDLESTRUCTURES1983}.
对terminal三位代数簇的完整证明由Corti给出，使用的是下降法。\cite{cortiFactoringBirationalMaps}.
由下降法的Sarkisov纲领归纳地构造Sarkisov连接。选取一个定义了双有理映射$\Phi:X \dashrightarrow X'$的线性系 $\mathcal{H}$ (或一个一般的除子 $H \in \mathcal{H}$)，那么第一个Sarkisov连接 $\psi_1:X\dashrightarrow X_1$ 由运行一种特殊的极小模型纲领得到，被称为 $2$-ray game，并且取决于 $\mathcal{H}$ ($H$) 的选取。接着用 $\Phi_{1}=\Phi\circ \psi_1^{-1}: X_1 \dashrightarrow X'$替代 $\Phi:X\dashrightarrow X'$并重复这一过程。 

Sarkisov次数$(\mu,\lambda,e)$可以度量两个森纤维空间的“距离”

The Sarkisov degree $(\mu,\lambda,e)$ is designed to prove the termination. The invariant (nef threshold) $\mu$ lies in a discrete set due  to the boundedness of Fano varieties. The invariants (canonical threshold) $\lambda$ and (the number of crepant divisors) $e$ are related to the singularities of $K_X$ with respect to $H$. 
The Sarkisov degree drops after the replacement, and the Sarkisov program terminates after finitely many steps. 
Bruno and Matsuki \cite{brunoLogSarkisovProgram1995} generalize this method to the case of $\mathbb{Q}$-factorial klt threefolds. Moreover, they outline the Sarkisov program for $\mathbb{Q}$-factorial klt pairs in any dimension.
After important advances in the minimal model program, such as the termination of the MMP with scaling \cite{BCHM10}, the ACC of lcts \cite{HMX14}, the boundedness of $\delta$-lc Fano varieties \cite{Bir19}, \cite{birkarSingularitiesLinearSystems2020}, the program they outlined works partially. The main remaining open question is related to the termination of flips and ascending chain condition (or finiteness) of local log canonical thresholds.
We call this approach the original method. We are not aware of detailed references discussing the original method for higher dimensional klt pairs, and therefore we discuss this in detail in Section 3. 

Using the finiteness of weak log canonical models established in \cite{BCHM10}, Hacon \cite{haconMinimalModelProgram2012} gives another approach to the Sarkisov program, which is called the double scaling method and is known to terminate in all dimensions. 
Both approaches construct the Sarkisov links by 2-ray games. 
But in this approach, a common log resolution $(W,B_W)$ of two Mori fibre spaces is fixed as the roof of the program such that each Sarkisov link is ``under the roof'', and each Mori fibre space in the Sarkisov links is a weak log canonical model of $W$. 
The termination of the method of double scaling can then be shown using techniques similar to the termination of flips with scaling.
Liu \cite{liuSarkisovProgramGeneralized2021} generalizes Hacon's method to generalized pairs.
 We introduce the double scaling method in Section 4.


Using the idea of Shokurov's polytopes \cite{Sho96}, \cite{cs11}, Hacon and M\textsuperscript{c}Kernan \cite{haconSarkisovProgram2012} give a different approach to the Sarkisov program without using 2-ray games.
Let $W$ be a common log resolution of $(X,B)\to S$ and $(X',B')\to S'$, then there are divisors $D$ and $D'$ on $W$ such that $S$ and $S'$ are ample models of $W$ for $K_W+D$ and $K_W+D'$ respectively. 
Moreover, there are some other divisors $D_i$ in the polytope of boundaries of $W$ corresponding to other Mori fibre spaces $X_i\to S_i$ and ample models $S_i$ of $W$. Then there is a path in the polytope connecting these divisors $D_i$ and it gives a decomposition of $\Phi$ into Sarkisov links.
Miyamoto \cite{miyamoto2019TheSP} uses this method to show that the Sarkisov program works for lc log surfaces or $\mathbb{Q}$-factorial log surfaces over an algebraically closed field of any characteristic. 
We call this approach the polytope method and introduce it in Section 5. 

In Section 6, we give examples to illustrate each method of the Sarkisov program.

The Sarkisov program has many applications, such as the classical result for the Cremona group of rank 2. That is, any birational automorphism of the projective plane is a composition of automorphisms of the projective plane and standard quadratic transforms (see \cite{ksc04} Chapter 2). Takahashi \cite{tak95} establishes the Sarkisov program for log surfaces and obtains another proof for the classical algebraic result: any automorphism of the affine plane is a composition of linear transformations and upper triangular transformations (see \cite{mat02}, Chapter 13). For more applications, we refer to \cite{lam22} by Lamy.

